Adaptative neigbouring methods applied to telephonic base stations

### 2024-08-19 article.tex
Ajout de la filtration de la base

    For that, it is necessary to describe and analyse the databases that have been used during the research, then to present 
    the different approaches that always consist of these steps : establish a first neighbouring graph, compute the base station 
    densities and filter this graph with different criteria using this information. The final step is to present the results
    of the different approaches and conclude.

    \textbf{WE WILL WORK WITH ONLY ONE PROVIDER [ptet le mettre ailleurs].}
\section{Related works}

@@

    \begin{table}[!b]
        \centering
        \caption{Summary of technologies}
        \label{table:techno_numbers}
        \begin{tabular}{cccccc}
            \toprule
            \textbf{Technology} & \textbf{Bouygues} & \textbf{Free} & \textbf{Orange} & \textbf{SFR} & \textbf{Total} \\
            \cmidrule(lr){1-6}
            \textbf{2G} & 21710 & 0 & 18835 & 20093 & 60638 \\
            \textbf{3G} & 26294 & 25934 & 29748 & 25777 & 107753 \\
            \textbf{4G} & 26231 & 25847 & 30440 & 25881 & 108399 \\
            \textbf{5G} & 11271 & 18607 & 8794 & 10968 & 49640 \\
            \textbf{Total} & 26331 & 25949 & 30540 & 26018 & 108838 \\
            \bottomrule
        \end{tabular}
    \end{table}

@@

>>>>

    For that, it is necessary to describe and analyse the databases that have been used during the research, then to present 
    the different approaches that always consist of these steps : establish a first neighbouring graph, compute the base station 
    densities and filter this graph with different criteria using this information. The final step is to present the results
    of the different approaches and conclude.
\section{Related works}

@@

    \begin{table}[!b]
        \centering
        \caption{Summary of technologies}
        \label{table:techno_numbers}
        \begin{tabular}{cccccc}
            \toprule
            \textbf{Technology} & \textbf{Bouygues} & \textbf{Free} & \textbf{Orange} & \textbf{SFR} & \textbf{Total} \\
            \cmidrule(lr){1-6}
            \textbf{2G} &You can 21710 & 0 & 18835 & 20093 & 60638 \\
            \textbf{3G} & 26294 & 25934 & 29748 & 25777 & 107753 \\
            \textbf{4G} & 26231 & 25847 & 30440 & 25881 & 108399 \\
            \textbf{5G} & 11271 & 18607 & 8794 & 10968 & 49640 \\
            \textbf{Total} & 26331 & 25949 & 30540 & 26018 & 108838 \\
            \bottomrule
        \end{tabular}
    \end{table}

@@

    \subsection{Filtering the database}
    As seen before this database is really huge, as a matter of fact we will only work on a portion of it.

    Firstly, only one provider will be kept because a \acrshort{bs} from provider $x$ can't be considered as a neighbour of \acrshort{bs} from provider $y$.
    Consequently, we have chosen \emph{Orange} because it is the one that has the largest number of \acrshort{bs}.

    Secondly, for the same reasons as before, only one technology is kept. Thus, we kept all \acrshort{bs} using, at least, $4G$.
